Panel Seminars

### 2023-08-27 ADMIN_01_submissions_instructions.Rmd
minor edits to protocol for developing content

### MarineOmics publishing process
#### Content development and review process
1. Initiation: The potential contributor contacts the website manager via email or the discussion forum with an idea.
<br>
2. Development: Meet with the website manager, Katherine Silliman and/or Sam Bogan (Working Group Co-leaders) <br>
    + All active members will be notified and invited to be involved in the review process. <br>
    + The contributor presents their idea for new material. <br>
    + There will be regular meetings (frequency decided by those involved) with the website manager, Katherine Silliman and/or Sam Bogan, and any other participating members for progress updates and support. <br>
3. Review: Full drafts of content will be reviewed by the website manager, Katherine Silliman and/or Sam Bogan, and at least one other active MarineOmics member assigned to the project.

>>>>

### MarineOmics publishing process
#### Content development and review process
1. Initiation: The potential contributor contacts the website manager via email  (jasonjohns[at]ucsb.edu) or the discussion forum with an idea.
<br>
2. Development: Meet with the website manager, Katherine Silliman and/or Sam Bogan (Working Group Co-leaders). <br>
    + All active members will be invited to be involved in the review process. <br>
    + The contributor presents their idea for new material to any involved working group members. <br>
    + There will be regular meetings (frequency decided by those involved) with the website manager, Katherine Silliman and/or Sam Bogan, and any other participating members for progress updates and support. <br>
3. Review: Full drafts of content will be reviewed by the website manager, Katherine Silliman and/or Sam Bogan, and at least one other active MarineOmics member assigned to the project.

### 2023-08-27 index.Rmd
minor edits to protocol for developing content

# How to Contribute
We are excited to incorporate new material from contributors of various backgrounds, expertise, and experience. To date these tutorials, guidelines,  and discussions have been authored and led by graduate students and postdocs with contributions from scientists at all levels, including undergraduates and faculty members. If you are interested in developing an information page or tutorial for the website, we ask that you review our [page with instructions for submitting content](ADMIN_01_submissions_instructions.html) and contact our Website Manager Jason Johns (jasonjohns[at]ucsb.edu).

>>>>

# How to Contribute
We are excited to incorporate new material from contributors of various backgrounds, expertise, and experience. To date these tutorials, guidelines,  and discussions have been authored and led by graduate students and postdocs with contributions from scientists at all levels, including undergraduates and faculty members. If you are interested in developing an information page or tutorial for the website, we ask that you review our [page with instructions for developing content](ADMIN_01_submissions_instructions.html) and contact our Website Manager Jason Johns (jasonjohns[at]ucsb.edu).
